Dispersion distance and the matter distribution of the Universe in dispersion space

### 2015-06-04 writeup/dm_space_distortions.tex
Added NSERC to acknowledgements.  Said 10000 is a modest amount of time for CHIME or SKA

We have
shown in Figure~\ref{f:sensitivity}
that a survey detecting $10000$ fast radio bursts of cosmological
origin could detect the
clustering signal. This is in rough
approximation to what might be achieved by the Canadian Hydrogen Intensity
Mapping Experiment (CHIME)\footnote{\url{http://chime.phas.ubc.ca/}}, the
Square Kilometer Array\footnote{\url{http://www.skatelescope.org/}},
or other upcoming wide-field telescopes.
Looking forward, dispersion-space
clustering could become a precision probe of large-scale structure should
observational factors turn out to be favourable compared to spectroscopic
surveys. The baryon acoustic oscillation feature can be clearly seen in
Figure~\ref{f:terms} in the cross term and both
local-term curves. It may also be possible to extract the BAO feature
from the integral
term using tomography.
This however requires that the contribution to dispersion from
the source's environment and host halo be small compared to the
contribution from the IGM.

@@

We thank Ue-Li Pen and Mathew McQuinn for helpful discussions.
%
KWM is supported by the Canadian Institute for Advanced Research, Global Scalars
Program.

>>>>

We have
shown in Figure~\ref{f:sensitivity}
that a survey detecting $10000$ fast radio bursts of cosmological
origin could detect the
clustering signal. This is in rough
approximation to what might be achieved in a modest amount of time by the Canadian Hydrogen Intensity
Mapping Experiment (CHIME)\footnote{\url{http://chime.phas.ubc.ca/}}, the
Square Kilometer Array\footnote{\url{http://www.skatelescope.org/}},
or other upcoming wide-field telescopes.
Looking forward, dispersion-space
clustering could become a precision probe of large-scale structure should
observational factors turn out to be favourable compared to spectroscopic
surveys. The baryon acoustic oscillation feature can be clearly seen in
Figure~\ref{f:terms} in the cross term and both
local-term curves. It may also be possible to extract the BAO feature
from the integral
term using tomography.
This however requires that the contribution to dispersion from
the source's environment and host halo be small compared to the
contribution from the IGM.

@@

We thank Ue-Li Pen and Mathew McQuinn for helpful discussions.
%
KWM is supported by the Canadian Institute for Advanced Research, Global Scalars
Program.  The research of KS is supported in part by a National Science and Engineering Research Council (NSERC) of Canada Discovery Grant.
